---
title: "Initial Korean covid 19"
author: "Sierra Lander"
date: "5/30/24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```

# Introduction

$H_0$ There is no difference between death rates depending on sex  

$H_A$ There is a difference between death rates depending on sex





### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?


# Methods

Result is a categorical variable, sex is categorical

result depends on sex, we use helper file cat~cat

# Results  


## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```



This bar chart shows that a higher percentage of men than women died from covid, and that a higher percentage of woman lived than men.
  



  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
The numerical summary shows that 98.7% of women lived whereas 97% of men lived and 1.4% of women died while 3% of men died.





## Inferential results 


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```



## Conclusions

